On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-10 manuscripts/PNAS/chazthm_pnas.tex
minor edits Lem 4 proof

Since $|T_1| > \bar m (\ell -1) + (p-1) \geq \bar m (\ell -1)$, the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate. Let $F_1$ be the preimage of this family under $\pi$.  By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements. Thus, $F_1$ is the star of some element $i_1 \in [m]$.  From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.  If $p > 1$, then define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains more than $(\bar m - 1)(\ell -1)$ sets, and produce by the same argument a (necessarily) different index $i_2$. Iterating $p = \bar{m} - \ell(\bar m - m)$ times this loop yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
\end{proof}
\begin{proof}[Proof of Lem.\ref{MainLemma}]
We begin by showing that: 
\begin{align}\label{eq2}
d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
\end{align}
Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}. Since $|S| = |\pi(S)|$, we have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}. Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.

>>>>

Since $|T_1| > \bar m (\ell -1) + (p-1) \geq \bar m (\ell -1)$, the pigeonhole principle also implies that there are at least $\ell$ elements of $T_1$ sharing the same first coordinate. Let $F_1$ be the preimage of this family under $\pi$.  By the assumption \eqref{cond}, the intersection of $F_1$ is nonempty, and in fact must contain exactly $\ell$ elements by regularity. 
%Thus, $F_1$ is the star of some element $i_1 \in [m]$.  
From the SIP, the intersection of sets in $F_1$ is $\{i_1\}$, which by \eqref{cond} implies that the intersection of $\pi(S)$ with $S \in F_1$ also contains exactly one element.  If $p > 1$, then define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains more than $(\bar m - 1)(\ell -1)$ sets, and produce by the same argument a (necessarily) different index $i_2$. Iterating $p = \bar{m} - \ell(\bar m - m)$ times this loop yields the desired $J = \{i_1, \ldots, i_p\} \subseteq [m]$.
\end{proof}
\begin{proof}[Proof of Lem.\ref{MainLemma}]
We begin by showing that: 
\begin{align}\label{eq2}
d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
\end{align}
Since the right-hand side of \eqref{GapUpperBound} is less than one (by \eqref{delrho} and $r \leq 1$), it follows from \eqref{dimLem} that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}. Since $|S| = |\pi(S)|$, we have $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$, and \eqref{eq2} follows using \eqref{eqdim}. Note that the columns of $\mathbf{B}_{\pi(S)}$ are therefore linearly independent, for all $S \in E$.
